R Notebook

### 2022-06-01 tutorials/sp-regress.Rmd
Adds notebook for experimenting with kronecker products for st modeling

@@

# Arrange in tbl
dat = tibble(loc.idx=rep(1:n,k), E=rep(coo[,1],k), N=rep(coo[,2],k), 
             Year=rep(1:k, each=n), y=c(y), yr.val = c(year.val))
```

@@

@@

dat.stack <- inla.stack(
  data = list(y = dat$y), 
  A = list(A0, A1, 1), 
  effects = list(i0, 
                 i1, 
                 tibble(Intercept = 1, mu1 = 1, 
                        Year=dat$Year)),
  tag = 'dat')

@@

```{r}
mod.2 = inla(form, family = 'gaussian',
           data = inla.stack.data(dat.stack), 
           control.predictor = list(A = inla.stack.A(dat.stack)), 
           control.inla = list(int.strategy = 'eb'), # no integr. wrt theta)
           control.compute = list(config=TRUE))
```

```{r}
# i=sample.int(max(dat$loc.idx), size=1)
# ggplot(dat %>% filter(loc.idx==i)) + geom_line(aes(x=Year, y=y))
```

>>>>

set.seed(4)
# Simulate the covariate values
hh <- runif(n * k) 
mu.beta <- c(400, -1)
taue <- 20

@@

# Arrange in tbl
dat = tibble(loc.idx=rep(1:n,k), E=rep(coo[,1],k), N=rep(coo[,2],k), 
             Year=rep(1:k, each=n), y=c(y))
```

@@

```{r}
mesh <- inla.mesh.2d(dat %>% select(E,N), max.edge = c(0.15, 0.3),
  offset = c(0.05, 0.3), cutoff = 0.07)
# mesh <- inla.mesh.2d(dat %>% select(E,N), max.edge = c(0.25, 0.5),
#   offset = c(0.05, 0.3), cutoff = 0.15)

@@

dat.stack <- inla.stack(
  # data = list(y = dat$y), 
  data = list(y = log(dat$y)),
  A = list(A0, A1, 1), 
  effects = list(i0, 
                 i1, 
                 tibble(Intercept = 1, mu1 = 1, 
                        Year=dat$Year)),
  tag = 'dat')

@@

```{r}
mod.2 = inla(form, family = 'gaussian',
           data = inla.stack.data(dat.stack), 
           # control.family = list(control.link=list(model='log')), 
           control.predictor = list(A = inla.stack.A(dat.stack)), 
           control.inla = list(int.strategy = 'eb'), # no integr. wrt theta)
           control.compute = list(config=TRUE))
```

```{r}
summary(mod.2)
# i=sample.int(max(dat$loc.idx), size=1)
# ggplot(dat %>% filter(loc.idx==i)) + geom_line(aes(x=Year, y=y))
```
